Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

>>>>

~\newline
\noindent\textbf{II. Parameters or Adjustable Items}

The only two tunables in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
They are further discussed in the previous section in this supplementary
material (see the ``Performance-Sensitive Factors'' part of the previous
section).

Since PGD~\cite{madry} is adopted for optimizing the objective of HM, the
PGD parameters (including perturbation budget $\varepsilon$, maximum step
$\eta$, as well as step size $\alpha$) will also influence the result.
%
We following the parameter setting following the state-of-the-art
defense~\cite{robrank} for fair comparison.
